\documentclass[12pt]{article}
\usepackage{graphicx}


\begin{document}

\title{The Great Adventures of
\\{\Huge {\textbf{BINNING}}}
\\
\bigskip
\small{Comedies, \\Histories, and \\Tragedies.}}
\author{Translated by Navraj Singh}
\maketitle 

\bigskip
\begin{tiny}
    \begin{center}
        \textit{This play was brought to you by BINNING LLC}
    \end{center}
\end{tiny}

\section*{The night of the fat daddy}
\subsection*{Scene 1, Act 1}
\begin{center}
    \textit{opening\\special guest Risham walks in\\cue audience clapping and whistling}
\end{center}

Risham
\begin{center}
    Hi. May I have 1 fat daddy please.\\
    \textit{\\audience laugh track}
\end{center}

Cashier 
\textit{*questioning face*} 
\begin{center}
    Yeaa…..anything else?
\end{center}

Risham
\begin{center}
    No just fat daddy
\end{center}
\begin{flushright}
    \textit{*Risham sits at table*}
\end{flushright}

\begin{center}
    *10 minutes goes by*\\*everyone’s get their food*
\end{center}

Risham
\textit{ angry}
\begin{center}
    EXCUSE ME BUT WHERE IS MY $FAT$ DADDY!
\end{center}

Cashier
\begin{center}
    S-s-s-sorry sir but it’s-
\end{center}

Risham
\begin{center}
    ENOUGH! I will banish u from my hood.\\I need my fat daddy before I edge u! 
\end{center}

Cashier
\begin{center}
    right away s-s-s-sir 
\end{center}

Risham
\begin{center}
    fuck outta here nigga
\end{center}

\begin{center}
    *audience ooooo noise*\\*2 mins pass by*\\*enter waiter*
\end{center}

Waiter
\begin{center}
    who ordered $fat$ little daddy?
\end{center}

Risham
\textit{ happy}
\begin{center}
    yes, I ordered the fat daddy.
\end{center}

Waiter
\begin{center}
    enjoy
\end{center}

Risham
\begin{center}
    finally I can enjoy my fat daddy.\\
    *audience claps*
\end{center}

Risham
\begin{center}
    mmmmm this fat daddy taste so goooddddd.\\
    *audience final laugh track*\\*cast bows*\\
    fin.
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{The Press of ‘24}
\subsection*{Scene 1, Act 2}
\begin{center}
    \textit{*Armaan Enter*}
\end{center}

Armaan
\textit{ angrily walks in}
\begin{center}
    You fucking bitch listen here!
\end{center}

Salayka
\textit{  with fear in his eyes}
\begin{center}
P-p-p-p-please….don’t hurt me
\end{center}

\begin{flushright}
    cries in desperation\\
\end{flushright}

\begin{center}
    *Armaan grabs salayka by his collar*\\
\end{center}

Salayka
\begin{center}
    PLEASE STOP
\end{center}

Armaan
\begin{center}
    Let me in the redhat or else
\end{center}

Salayka
\begin{center}
    P-please let me go I’ll add u rn
\end{center}

\begin{flushright}
    sweating perfusouley in fear
\end{flushright}

Armaan
\begin{center}
    yea you $bitch!$\\
\end{center}

\begin{center}
    \textit{*Armaan drops salayka to the ground,*\\salayka falls and tries to catch his breath*}
\end{center}

Armaan
\textit{ smug}
\begin{center}
    Thats what I thought\\Get up and do ur job $baldy$
\end{center}

Salayka
\textit{  fear in his eyes}
\begin{center}
    Yes boss
\end{center}
\begin{flushright}
    quickly types on his keyboard\\
\end{flushright}

\begin{center}
    \textit{*Armaan walks away*}\\
    fin.
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Backdoor Betrayal}
\subsection*{Scene 1, Act 3}
\begin{center}
    \textit{*Backdoor opens*\\~\\~*Risham walks in*\\~*audience laughs*\\~\\~*Mahdi Walks in*\\*audience claps*}
\end{center}

Risham
\begin{center}
    Mahdi, do you-
\end{center}
\begin{flushright}
    walks to first row of seats
\end{flushright}

Mahdi
\textit{  seeing opportunity}
\begin{flushright}
    quickly rushes to a \\open seat next to shorty
\end{flushright}

Risham
\textit{  confused}
\begin{center}
    \textit{*YELLS*} 
    Mahdi, why are you sitting $there$?
\end{center}

Mahdi
\textit{  embarrased}
\begin{center}
    ...\\
    So, I can easily get up and leave
\end{center}
\begin{flushright}
    Points at leg and crutches\\Face hot red from embarrasement
\end{flushright}

\smallskip

\begin{center}
    *audience gasps*
\end{center}

\smallskip

\begin{center}
    \textit{...time passes...}
\end{center}

Mahdi
\textit{  to further the quest he started}
\begin{center}
    It's so hot in here---\\
\end{center}

\smallskip 

Risham
\textit{  swiftly turns, illmannered}
\begin{center}
    \textbf{Who are \textit{you} talking to?}
\end{center}
\begin{flushright}
    squinting his eyes\\talking disrespectfully
\end{flushright}

Mahdi
\textit{  struct with Betrayal}
\begin{flushright}
    Mouth opens but no noise\\
    Looks at Risham with a look of betrayal\\
    \tiny{Inner Monologue:} \textit{I thought we were friends}
\end{flushright}
\begin{center}
    sigh.
\end{center}

Audience
\begin{center}
    *audience laughs*\\
    Risham you so funny\\
    fin.
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{The Frosty Fright of '23}
\subsection*{Scene 1, Act 4}
\smallskip
\begin{center}
    \tiny{Due to limited information and translation,\\true events may have been altered.}
\end{center}

\begin{center}
    \textit{Context: Risham, Armaan, and Nav come back from Wendy's Run.\\Our characters are walking to class.}
\end{center}

Risham
\textit{  with a smile}
\begin{center}
    I'm so happy I got my frosty\\It's so good
\end{center}

Armaan
\textit{  worried}
\begin{center}
    Let's hurry up guys we're gonna be late
\end{center}

Nav
\textit{  looking at girls}
\begin{center}
    Damn, they so bad...
\end{center}
\begin{flushright}
    Completely entraced with the girls' beauty\\
\end{flushright}

\begin{center}
    *Risham takes a bite of his frosty*\\*audience laughs*\\*Risham trips and drops frosty*\\*audience gasps*\\*Risham looks at the ground*\\*audience laughs*\\*Risham looks at Armaan*\\*audience laughs*\\*Risham looks at Nav*\\*audience laughs*\\
\end{center}

Nav
\textit{  embarrased}
\begin{center}
    \textbf{RISHAM!} Why would you drop the \\frosty \textit{infront} of the bad bitches?!?
\end{center}
\begin{flushright}
    Runs away because of sheer embarrasement
\end{flushright}

Armaan
\textit{  confused}
\begin{center}
    Nav? \textit{Where} are the so called bad bitches?
\end{center}

Nav
\textit{  from a distance}
\begin{center}
    \textit{*yells*} Right there! In Saltan!
\end{center}

Armaan and Risham
\textit{  in unison}
\begin{center}
    \textit{*looks at each other* } 
    \textbf{Saltan?}
\end{center}

Armaan
\textit{  laughing}
\begin{center}
    \textit{*laughs*\\} 
    Nav, you're so dumb.\\Those are mid white girls\\
    \textit{*laughs*} 
\end{center}

\smallskip
\begin{center}
    *Nav runs away from embarrasement*\\*Audience claps*\\*Cast bows*\\~\\fin.
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Great Gaslighting}
\subsection*{Scene 2, Act 4}
\smallskip
\begin{center}
    \tiny{Due to limited information and translation,\\true events may have been altered.}
\end{center}

\begin{center}
    \textit{Context: Risham, Armaan, and Nav are in class.}
\end{center}

Risham
\textit{  trolling}
\begin{center}
    \textit{*laughs*} 
    Nav, why did you drop the frosty cup?\\
    \textit{*laughs*}
\end{center}

Nav
\textit{  confused}
\begin{center}
    I didn't drop the frosty cup---
\end{center}

Armaan
\textit{  laughing}
\begin{center}
    No! Nav you dropped it!
\end{center}

Nav
\textit{  defending himself}
\begin{center}
    No, I didn't drop it!\\
    \textit{*looks at Risham*}\\
    Risham Did!\\
    I have lactose intolerance\\I can't eat frosty!\\
\end{center}

\begin{center}
    The three characters go back and forth\\and try to gaslight nav into thinking he dropped the frosty\\*audience laughs*\\
\end{center}

Nav
\textit{  defeated}
\begin{center}
    \textit{*sighs*} 
    I guess I did drop the frosty\\
    \textit{*sighs*}
\end{center}

\begin{center}
    *audience laughs*\\*Cast bows*\\~\\fin.
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\end{document}